Wave functions in phase space

### 2017-11-24 pra-0-1.tex
add some thoughts on phase space wave functions

Numerical analysis.  How to expand a wave function over Lagrange(?) polynomials.

@@

>>>>

Numerical analysis.  How to expand a wave function over Hermite polynomials.  I.e., is there a matrix A_n and points x₁ through x_n, such that A_n·(f(x₁) ⋯ f(x_n))' gives the components of the Hermite functions H₁ through H_n in f, and is exactly right for H₁ through H_n?  (And therefor for linear combinations of them?)  This is almost certainly Gauss-Hermite quadrature, because e^{-x²}·e^{-x²}=e^{-2x²}, and the Gauss-Hermite formula is exact for e^{-x²}·P(x) with P a low-order polynomial.

@@

Plots of how tunnelling looks in phase space over time.  If we start off with a real wave packet in one side of a double well, how does it get momentum to tunnel to the other side?
